Designing a high-performance boundary element library with OpenCL and Numba

### 2021-03-29 bem.tex
Finished most of the OpenCL section.

\begin{figure}
	\center
	\includegraphics[width=5cm]{img/sphere}
	\label{fig:triangulation}
	\caption{Discretisation of a sphere into flat surface triangles.}
\end{figure}

@@

In summary, to solve a boundary integral equation problem, the following steps are performed by Bempp
\begin{enumerate}
	\item Import of the surface description as triangulation data
	\item Definition of the trial space, test space and range space
	\item Discretization into a matrix problem $Ax=b$
	\item Evaluation of domain potential operators for visualization and post-processing
\end{enumerate}

>>>>

\begin{figure}
	\center
	\includegraphics[width=5cm]{img/sphere}
	\caption{Discretisation of a sphere into flat surface triangles.}
		\label{fig:triangulation}

\end{figure}

@@

In summary, to solve a boundary integral equation problem, the following steps are performed by Bempp
\begin{enumerate}
	\item Import of the surface description as triangulation data.
	\item Definition of the trial space, test space and range space.
	\item Discretization into a matrix problem $Ax=b$.
	\item Solution of the matrix problem by either a direct or iterative solver.
	\item Evaluation of domain potential operators for visualization and post-processing.
\end{enumerate}
